Playing against Nature: causal discovery for decision making under uncertainty

### 2018-05-16 Segundo_Semestre/CausalML_Workshop/Paper_long_version.tex
explicando el modelado como un juego en la intro

Learning by interaction has been extensively studied by computer scientists using the Reinforcement Learning  setting \cite{sutton1998reinforcement}, but the most common used techniques  in this field are purely reactive and do not consider any high-level structure of the environment beyond what is expressable in a Markov Decision Process (\cite{garnelo2016towards}).

Since human beings are known to learn causal graphical models in sequential decision making processes (\cite{sloman2006causal}, \cite{nichols2007decision}, \cite{meder2010observing}, \cite{hagmayer2013repeated}, \cite{danks2014unifying}), although this learning is not perfect (\cite{rottman2014reasoning}) ,we propose that an autonomous agent can learn and use causal information while interacting with an uncertain environment which is governed by a fixed \textit{causal mechanism} unknown to the agent.

The interaction between the decision maker and his environment is modelled as a repeated game with incomplete information between a player called Nature which selects his actions from the causal model and the decision maker and propose a way for the agent to have \textit{beliefs} about the causal model that governs the environment.

>>>>

Learning by interaction has been extensively studied by computer scientists using the Reinforcement Learning (RL) setting \cite{sutton1998reinforcement}, but the most common used techniques  in this field are purely reactive and do not consider any high-level structure of the environment beyond what is expressable in a Markov Decision Process (\cite{garnelo2016towards}).

Since human beings are known to learn causal graphical models in sequential decision making processes (\cite{sloman2006causal}, \cite{nichols2007decision}, \cite{meder2010observing}, \cite{hagmayer2013repeated}, \cite{danks2014unifying}), although this learning is not perfect (\cite{rottman2014reasoning}), we propose that an autonomous agent can learn and use causal information while interacting with an uncertain environment which is governed by a fixed \textit{causal mechanism} unknown to the agent.

The proposed way for an agent to learn from repeated interactions is by giving her \textit{beliefs} about the structure of the environment in form of a probability distribution over a suitable space. This beliefs will be updated according with what is observed.

While the standard setting in RL is to model the interaction agent-environment as an agent moving from one \textit{state} to another and observing a reward, we propose to model it as a \textit{game} between the decision maker and a player called Nature which will select his actions from the causal model.
